PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-08-26 reviews/softwarex/reviews_1/response/response.tex

\newenvironment{response}{\vspace{1em}\noindent\textbf{Response}}{\vspace{1em}}

\begin{document}
We would like to thank the reviewers for their comments. Below we provide
a response to their specific remarks.

\section{Reviewer 1}

\begin{enumerate}
  \item The cross-entropy benchmarking technique used in the validation of the Sycamore-53 QPU in
    quantum supremacy experiments (https://www.nature.com/articles/s41586-019-1666-5) should also
    be mentioned in the Introduction (https://www.nature.com/articles/s41567-018-0124-x).

    \begin{response} We modified manuscript to include mention of cross-entropy benchmarking as
      suggested by the referee.
    \end{response}
  \item The generalization of the suggested benchmarking techniqiue to multiple qubits should be
    described in more detail, explicitly mentioning whether the complexity of the derivation and
    actual benchmarking depends on the number of qubits.

    \begin{response} We thank the referee for this suggestion. We extended the manuscript with a
      paragraph describing differences between a single--qubit and higher-dimensional cases.
    \end{response}

### 2023-08-26 txt/manuscript_short.tex
Fix typos and grammar issues

Compared to these approaches, our approach allows for very simple operational
interpretation of the scheme and its results. This is especially useful for
newcomers to the field, who may be put off by more complicated appraoches.
Another benefit is, epsecailly for advanced users, the ability to control
resources utilized during the benchmarking. We can consider here resources such
as entanglement or coherence. Finally, the figure of merit we wish calculate and
to which we compare are results is fairly simple to obtain. The main downside of
our approach is the exponential number of circuits we need to consider.

>>>>

Compared to these approaches, our approach allows for a very simple operational
interpretation of the scheme and its results. This is especially useful for
newcomers to the field, who may be put off by more complicated approaches.
Another benefit is, especially for advanced users, the ability to control
resources utilized during the benchmarking. We can consider here resources such
as entanglement or coherence. Finally, the figure of merit we wish to calculate and
to which we compare the results is fairly simple to obtain. The main downside of
our approach is the exponential number of circuits we need to consider.
